%\cvsection{Publications}
\vspace{+2mm}\centering{\color{awesome-darknight}\textbf{\large{References}}}\vspace{-3mm}
\rule{\textwidth}{0.5pt}\vspace{-1mm}

\begin{cventries}
\vspace{-4mm}
%------------------------------------------------

\cventry
{} % Degree
{} % Institution
{} % Location
{} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item{``He obtained in my course a final mark of 30/30 cum laude. Thus, 
his results compared to those of his peers are excellent and his intellectual 
abilities are such to position him within the top 5\% students. Moreover 
he worked with enthusiasm on this subject and demonstrated autonomy and 
initiative in implementing new features in the architecture [of the final 
project] in order to improve its performance. I noticed optimal initiative and 
fantasy in conceiving alternative architectural solutions.''.\newline
\hspace*{\fill}\textbf{Prof. Mariagrazia Graziano}, Microelectronic Systems 
module, Politecnico di 
Torino.\hspace{+6mm}\vspace{+4mm}}
\item{``Mr. De Gennaro is an outstanding individual with a strong 
character. He has the ability to produce impressive results in a wide variety 
of areas. He is very motivated and has set high goals for his life. During my 
course, his laboratory homework was always precise and exhaustive. 
[..]''.\newline
\hspace*{\fill}\textbf{Prof. Pietro Laface}, Operating Systems module, 
Politecnico di Torino.\hspace{+6mm}\vspace{+4mm}}
\item{``During the lectures and the lab work I have witnessed the rapid growth 
of his design skills, achieved thanks to a constant effort in the laboratory 
activities, and his deep and spontaneous interest in the subjects. He passed 
the exam with final mark 30/30, corresponding to Grade A.''\newline
\hspace*{\fill}\textbf{Prof. Paolo Camurati}, Specification and Simulation of 
Digital Systems module, Politecnico di Torino.\hspace{+6mm}\vspace{+0.1mm}}
\end{cvitems}
}
\end{cventries}\vspace{-3mm}